Manuscript Code

### 2022-10-10 Manuscript Code.Rmd
Updating redlining area calculations and block counts

pacman::p_load(dplyr, ggplot2, ggpubr, sf, tidyverse, modelr, nlme, gstat, sp, geepack, kableExtra)

@@

outside_redlining <- subset(census_preds_wide, !(census_preds_wide$block_key %in% redlining_blocks$block_key))

## n Blocks
nrow(census_preds_wide)
length(unique(redlining_blocks$block_key))
nrow(census_preds_wide) - length(unique(redlining_blocks$block_key))
redlining_blocks %>%
  group_by(holc_grade) %>%
  summarise(pop = sum(1/count))

@@

## Pollutants and demographics
summary(census_preds_wide)
summary(data.frame(unique(redlining_blocks)))
summary(outside_redlining)
summary(subset(redlining_blocks, holc_grade == "A"))
summary(subset(redlining_blocks, holc_grade == "B"))
summary(subset(redlining_blocks, holc_grade == "C"))
summary(subset(redlining_blocks, holc_grade == "D"))
summary(subset(redlining_blocks, holc_grade == "X"))

@@

## Redlining region area
redlining_blocks_unique <- subset(redlining_blocks, !duplicated(redlining_blocks$block_key))
redlining_block_areas <- redlining_blocks_unique %>%
  left_join(all_block_areas, by=c("block_key"="BLOCKID10"))
sum(redlining_block_areas$area/1000000)

## Redlining grades area
redlining_grades_areas <- redlining_blocks %>%
  left_join(all_block_areas, by=c("block_key"="BLOCKID10"))
redlining_grades_areas$adj_area <- redlining_grades_areas$area/redlining_grades_areas$count
sum(redlining_grades_areas[redlining_grades_areas$holc_grade == "A", ]$adj_area/1000000)
sum(redlining_grades_areas[redlining_grades_areas$holc_grade == "B", ]$adj_area/1000000)
sum(redlining_grades_areas[redlining_grades_areas$holc_grade == "C", ]$adj_area/1000000)
sum(redlining_grades_areas[redlining_grades_areas$holc_grade == "D", ]$adj_area/1000000)
sum(redlining_grades_areas[redlining_grades_areas$holc_grade == "X", ]$adj_area/1000000)

@@

coordinates(df_resids_locs) = ~longitude+latitude
vario = variogram(resids_pnc~longitude+latitude, df_resids_locs)
plot(vario)

@@

ggplot(data=fig_4, aes(x=race_eth_grp, y=estimate*5, ymin=conf.lo*5, ymax=conf.hi*5)) +
  geom_pointrange(aes(col=race_eth_grp)) + 
  geom_hline(aes(col=race_eth_grp), yintercept=0, linetype=2) +
  xlab("Pollutant") + ylab("Mean Difference (95% CI) per 5% Increase in Population") + 
  geom_errorbar(aes(ymin=conf.lo*5, ymax=conf.hi*5, col=race_eth_grp), width=0.5 ,cex=1) + 
  facet_wrap(~factor(variable, levels=c("UFP (pt/cm3)","BC (ng/m3)","NO2 (ppb)","PM2.5 (µg/m3)")), strip.position="left", nrow=4, scales = "free_x") +
  geom_blank(aes(y = low)) +
  geom_blank(aes(y = high)) +
  theme(plot.title=element_text(size=16,face="bold"),
      axis.text.y=element_blank(),
      axis.ticks.y=element_blank(),
      axis.text.x=element_text(face="bold"),
      axis.title=element_text(size=12,face="bold"),
      strip.text.y = element_text(hjust=0,vjust = 1,angle=180,face="bold")) +
  labs(color="Race-Ethnicity") +
  coord_flip()

@@

>>>>

pacman::p_load(dplyr, ggplot2, ggpubr, sf, tidyverse, modelr, nlme, gstat, sp, geepack, kableExtra, data.table)

@@

## n Blocks
nrow(census_preds_wide)
length(unique(redlining_blocks$block_key))
nrow(census_preds_wide) - length(unique(redlining_blocks$block_key))

@@

## Pollutants and demographics
summary(census_preds_wide)
summary(data.frame(unique(redlining_blocks)))
summary(subset(redlining_blocks, holc_grade == "A"))
summary(subset(redlining_blocks, holc_grade == "B"))
summary(subset(redlining_blocks, holc_grade == "C"))
summary(subset(redlining_blocks, holc_grade == "D"))
summary(subset(redlining_blocks, holc_grade == "X"))

@@

## Redlining region area and n blocks
kaya_areas <-  read.csv("/projects/trap/transfer/kaya/Code Review/redlining_areas_kb.csv")
all_graded2 <- read_csv("/projects/trap/transfer/kaya/9_30_area_definitions.csv")
all_graded2$bk_area <- all_graded2$area
all_graded2$intersect_area <- all_graded2$area2

setDT(kaya_areas)
kaya_areas$BLOCKID10 <- as.character(kaya_areas$block_key)
all_graded2$BLOCKID10 <- as.character(all_graded2$BLOCKID10)
k1 <- kaya_areas[,list(tot_area = sum(area),
                       n = length(area)), by = BLOCKID10]
k2 <- kaya_areas[,list(grade_area = sum(area),
                       grade_pct = sum(percent),
                       n = length(area)), by = c("BLOCKID10", "holc_grade")]
k2[,sum(grade_area/(1000*1000)),by = "holc_grade"]
k3 <- k2[,list(tot_area = sum(grade_area),
               tot_pct  = sum(grade_pct),
               n = length(grade_area)), by = "BLOCKID10"]
m_areas <- merge(k2[,c("BLOCKID10","holc_grade","grade_area","grade_pct")],
                 all_graded2[,c("BLOCKID10","bk_area","holc_grade","intersect_area")],
                 by = c("BLOCKID10", "holc_grade"), all = TRUE)
m_areas2 <- merge(m_areas, k3, by = "BLOCKID10")
m_areas2$best_area <- m_areas2$grade_pct * as.numeric(m_areas2$bk_area/(1000*1000))
m_areas2[,list(tot_area = sum(best_area, na.rm = TRUE)), by = "holc_grade"]
m_areas2[,list(tot_area = sum(best_area, na.rm = TRUE)), by = "holc_grade"]
sum(m_areas2$best_area, na.rm = TRUE)

m <- merge(k2, k3, by = "BLOCKID10")

# Table of split blocks
table(m[,c("holc_grade","n.y")])

@@

coordinates(df_resids_locs) = ~longitude+latitude
#vario = variogram(resids_pnc~longitude+latitude, df_resids_locs)
#plot(vario)

@@

ggplot(data=fig_4, aes(x=race_eth_grp, y=estimate*5, ymin=conf.lo*5, ymax=conf.hi*5)) +
  geom_pointrange(aes(col=race_eth_grp, shape=race_eth_grp)) +
  scale_shape_manual(values = c(15, 16, 17, 18)) + 
  scale_color_viridis_d() +
  geom_hline(aes(col=race_eth_grp), yintercept=0, linetype=2) +
  xlab("Pollutant") + ylab("Mean Difference (95% CI) per 5% Increase in Population") + 
  geom_errorbar(aes(ymin=conf.lo*5, ymax=conf.hi*5, col=race_eth_grp), width=0.5 ,cex=1) + 
  facet_wrap(~factor(variable, levels=c("UFP (pt/cm3)","BC (ng/m3)","NO2 (ppb)","PM2.5 (µg/m3)")), strip.position="left", nrow=4, scales = "free_x") +
  geom_blank(aes(y = low)) +
  geom_blank(aes(y = high)) +
  theme(plot.title=element_text(size=16,face="bold"),
      axis.text.y=element_blank(),
      axis.ticks.y=element_blank(),
      axis.text.x=element_text(face="bold"),
      axis.title=element_text(size=12,face="bold"),
      strip.text.y = element_text(hjust=0,vjust = 1,angle=180,face="bold")) +
  labs(color="Race-Ethnicity") + 
  guides(shape = "none") +
  coord_flip()

@@

redlining_blocks_unique <- subset(redlining_blocks, !duplicated(redlining_blocks$block_key))
